\documentclass{slate-resume}

\begin{document}

\slatemeta{John Doe CV}{John Doe}{Curriculum Vitae}{robotics, perception, legged locomotion}
\slateheader{John Doe}{1-555-000-0000\sep\href{mailto:john@example.com}{john@example.com}}{\href{https://www.example.com}{www.example.com}}

\section{Research Interests}
\begin{entryblock}
Legged robot locomotion, real-time perception and sensor fusion, autonomous navigation in unstructured environments, 3D scene understanding, and energy-efficient motion planning for mobile robotic systems.
\end{entryblock}

\section{Education}
\begin{entryblock}
\educationentry{Doctor of Philosophy, Robotics \textup{(in progress)}}{Aug 2026 - Present}{Carnegie Mellon University, Robotics Institute}
Advisor: Prof. Jane Smith. Dissertation: \textit{Adaptive Perception and Locomotion for Legged Robots in Unstructured Terrain.}
\end{entryblock}
\entrygap
\begin{entryblock}
\educationentry{Master of Science, Robotics}{Aug 2024 - May 2026}{Carnegie Mellon University, School of Computer Science}
GPA: 4.0/4.0. Thesis: \textit{Real-Time Semantic Segmentation for Legged Robot Navigation.}
\end{entryblock}
\entrygap
\begin{entryblock}
\educationentry{Bachelor of Science, Mechanical Engineering}{Aug 2020 - May 2024}{Georgia Institute of Technology, College of Engineering}
GPA: 3.92/4.0. Minor in Computer Science. Graduated with Highest Honors.
\end{entryblock}

\section{Research Experience}
\begin{entryblock}
\experienceentry{Graduate Research Assistant}{CMU Robotics Institute}{Pittsburgh, PA}{Aug 2024 - Present}
\begin{itemize}
  \item Developing a unified perception framework for legged robots that fuses LiDAR, stereo vision, and tactile sensing to estimate terrain deformability and adapt gait parameters in real time.
  \item Designing hierarchical reinforcement learning policies for quadruped locomotion on granular and deformable surfaces, demonstrating 40\% reduction in energy expenditure versus baseline gaits.
  \item Co-supervising two MS students on subprojects related to multi-modal sensor calibration and online terrain classification.
  \item Maintaining lab compute infrastructure across a 12-node GPU cluster, including Slurm scheduling and experiment reproducibility tooling.
\end{itemize}
\end{entryblock}
\entrygap
\begin{entryblock}
\experienceentry{Undergraduate Research Assistant}{Georgia Tech LIDAR Lab}{Atlanta, GA}{Jan 2023 - May 2024}
\begin{itemize}
  \item Built a custom dataset of 12,000 annotated point clouds for outdoor scene segmentation, establishing a benchmark adopted by three partnering institutions.
  \item Trained transformer-based 3D object detection models on multi-GPU clusters, achieving a 7\% improvement in mean average precision over baseline architectures.
  \item Authored internal documentation and reproducible training scripts used by 15 lab members across two research groups, standardizing experiment tracking with Weights \& Biases.
  \item Presented research progress at two internal lab symposia and one departmental poster session attended by faculty and industry sponsors.
\end{itemize}
\end{entryblock}
\entrygap
\begin{entryblock}
\experienceentry{Research Intern}{MIT CSAIL}{Cambridge, MA}{May 2023 - Aug 2023}
\begin{itemize}
  \item Investigated sim-to-real transfer strategies for contact-rich manipulation tasks, reducing the policy performance gap between simulation and physical hardware from 31\% to 9\%.
  \item Implemented domain randomization pipelines in Isaac Gym, parameterizing friction, mass, and actuator delay distributions across 200 randomized environment configurations.
  \item Contributed to an open-source benchmarking suite for dexterous manipulation policies, subsequently used in three published comparisons.
\end{itemize}
\end{entryblock}

\section{Industry Experience}
\begin{entryblock}
\experienceentry{Robotics Software Engineer Intern}{Boston Dynamics}{Waltham, MA}{May 2025 - Aug 2025}
\begin{itemize}
  \item Implemented real-time obstacle avoidance algorithms for quadruped locomotion across uneven terrain, reducing collision events by 34\% during field trials in warehouse environments.
  \item Designed a ROS2-based sensor fusion pipeline integrating LiDAR, stereo vision, and IMU data to improve localization accuracy from 15cm to under 3cm drift per kilometer.
  \item Wrote comprehensive unit and integration tests for the perception stack, increasing code coverage from 52\% to 89\% and catching three critical race conditions before deployment.
\end{itemize}
\end{entryblock}
\entrygap
\begin{entryblock}
\experienceentry{Mechatronics Engineering Intern}{Rivian}{Normal, IL}{May 2022 - Aug 2022}
\begin{itemize}
  \item Developed automated calibration routines for battery management system sensors across 40 pre-production vehicles, reducing manual calibration time from 6 hours to 45 minutes per unit.
  \item Built a Python-based diagnostic dashboard that aggregated CAN bus telemetry in real time, enabling technicians to identify faulty modules 60\% faster during assembly line audits.
  \item Collaborated with the thermal management team to validate coolant flow sensor readings against simulation models, identifying a systematic 4\% bias that led to a revised sensor placement strategy.
\end{itemize}
\end{entryblock}

\section{Publications}

\textit{* denotes equal contribution.}

\begin{entryblock}
\publicationentry{\underline{John Doe}, Marcus Rivera, Priya Chandrasekaran}{Real-Time Semantic Segmentation of Unstructured Terrain for Legged Robot Navigation}{IEEE International Conference on Robotics and Automation (ICRA), 2026}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{Priya Chandrasekaran, \underline{John Doe}, Wei Zhang}{Lightweight Transformer Architectures for On-Device 3D Object Detection}{Under review at IEEE Robotics and Automation Letters (RA-L), 2026}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{Marcus Rivera, Wei Zhang, \underline{John Doe}}{A Comparative Study of Visual Odometry Methods for GPS-Denied Quadruped Locomotion}{Submitted to Conference on Robot Learning (CoRL), 2026}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{Wei Zhang, \underline{John Doe}, Priya Chandrasekaran, Sarah Kim}{Adaptive Gait Generation for Legged Robots Using Reinforcement Learning on Deformable Surfaces}{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2025}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{\underline{John Doe}, Wei Zhang}{Multi-Resolution Point Cloud Registration for Large-Scale Outdoor Mapping}{Submitted to Robotics and Autonomous Systems, 2026}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{Sarah Kim, Marcus Rivera, \underline{John Doe}, Priya Chandrasekaran}{Energy-Efficient Motion Planning for Battery-Constrained Mobile Robots in Dynamic Environments}{IEEE Transactions on Robotics (T-RO), 2025}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{\underline{John Doe}, Sarah Kim}{Terrain-Aware Foothold Planning for Quadrupeds Using Sparse Depth Estimation}{Workshop on Legged Robots, ICRA, 2025}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{Marcus Rivera, \underline{John Doe}}{Online Extrinsic Calibration Between LiDAR and Stereo Camera for Mobile Robots}{IEEE Sensors Letters, 2024}
\end{entryblock}

\section{Projects}
\begin{entryblock}
\projectentry{Atlas}{Autonomous drone navigation system with visual SLAM.}{C++, Python}
\begin{itemize}
  \item Engineered a monocular visual SLAM pipeline capable of mapping indoor environments at 30fps on embedded NVIDIA Jetson hardware with sub-5cm positional error.
  \item Integrated a lightweight path planner that dynamically reroutes around newly detected obstacles within 200ms, tested across 50 unique indoor floorplans.
\end{itemize}
\end{entryblock}
\entrygap
\begin{entryblock}
\projectentry{Forge}{Custom 3D printing slicer optimized for multi-material extrusion.}{Rust}
\begin{itemize}
  \item Developed a parallel slicing engine that processes complex multi-body STL files 3$\times$ faster than conventional open-source alternatives while maintaining sub-layer accuracy.
  \item Implemented automatic support structure generation using voxel-based overhang detection, reducing failed prints by 22\% across a test suite of 200 models.
\end{itemize}
\end{entryblock}
\entrygap
\begin{entryblock}
\projectentry{Pulse}{Wearable biometric dashboard with real-time anomaly detection.}{Go, TypeScript}
\begin{itemize}
  \item Built a streaming data pipeline ingesting heart rate, SpO2, and accelerometer data from BLE devices, surfacing anomalies via a responsive web dashboard within 500ms.
  \item Designed a rolling-window statistical model that flags irregular cardiac rhythms with 91\% sensitivity, validated against 4,000 annotated sessions.
\end{itemize}
\end{entryblock}

\section{Teaching}
\begin{entryblock}
\experienceentry{Teaching Assistant, 16-833 Robot Localization and Mapping}{CMU}{Pittsburgh, PA}{Spring 2025}
\begin{itemize}
  \item Held weekly office hours for a 60-student graduate course covering SLAM, particle filters, and graph-based optimization.
  \item Designed two new programming assignments on factor graph SLAM and LiDAR odometry, now part of the permanent course curriculum.
\end{itemize}
\end{entryblock}
\entrygap
\begin{entryblock}
\experienceentry{Teaching Assistant, ME 2110 Creative Decisions and Design}{Georgia Tech}{Atlanta, GA}{Fall 2023}
\begin{itemize}
  \item Mentored eight student teams in a semester-long mechatronics design competition, providing guidance on mechanical design, embedded systems, and control.
  \item Evaluated weekly milestone reports and gave structured feedback to improve technical writing and presentation skills.
\end{itemize}
\end{entryblock}

\section{Honors \& Awards}
\begin{entryblock}
\educationentry{NSF Graduate Research Fellowship}{2024 - 2027}{National Science Foundation}
\end{entryblock}
\entrygap
\begin{entryblock}
\educationentry{Best Paper Award, Legged Robots Workshop}{ICRA 2025}{IEEE Robotics and Automation Society}
\end{entryblock}
\entrygap
\begin{entryblock}
\educationentry{President's Undergraduate Research Award}{Spring 2023}{Georgia Institute of Technology}
\end{entryblock}
\entrygap
\begin{entryblock}
\educationentry{Dean's List}{2020 - 2024}{Georgia Institute of Technology}
\end{entryblock}

\section{Talks \& Presentations}
\begin{entryblock}
\publicationentry{\underline{John Doe}}{Real-Time Terrain Segmentation for Legged Robots}{Invited talk, CMU RI Seminar Series, November 2025}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{\underline{John Doe}, Marcus Rivera}{Visual Odometry for GPS-Denied Environments}{Poster, Georgia Tech Research Symposium, April 2024}
\end{entryblock}
\entrygap
\begin{entryblock}
\publicationentry{\underline{John Doe}}{Sim-to-Real Transfer for Contact-Rich Manipulation}{Lightning talk, MIT CSAIL Student Symposium, August 2023}
\end{entryblock}

\section{Professional Service}
\begin{entryblock}
\textbf{Reviewer:} IEEE Transactions on Robotics (T-RO), IEEE RA-L, ICRA 2025, IROS 2025, CoRL 2025\\
\textbf{Student Volunteer:} ICRA 2025, IROS 2024\\
\textbf{Member:} IEEE Robotics and Automation Society, ACM
\end{entryblock}

\section{Technical Skills}
\begin{entryblock}
\skillentry{Languages}{Python, C++, Rust, Go, TypeScript, MATLAB, SQL, Bash, \LaTeX}
\skillentry{Frameworks}{ROS2, PyTorch, TensorFlow, OpenCV, Isaac Gym, React, Docker, Kubernetes}
\skillentry{Hardware}{NVIDIA Jetson, Raspberry Pi, Arduino, STM32, ZED Stereo Camera, Velodyne LiDAR}
\skillentry{Tools}{Git, Weights \& Biases, Slurm, CMake, GDB, Valgrind}
\end{entryblock}

\section{References}
\begin{entryblock}
Available upon request.
\end{entryblock}

\end{document}
